Supplementary information

### 2024-04-24 paper/supplementary_figures.Rmd
Update manuscript results, discussion and methods

@@

```{r}
tar_read(tab_sem_coeff) %>%
  kable(booktabs = TRUE,
    format = "latex",
    caption = "Standardised estimates from the Structural Equation Model
    displayed in main text (Fig. 2).",
    label = "sem-coeff"
    ) %>%
collapse_rows(columns = 1, latex_hline = "major", valign = "middle") %>%
kable_styling(latex_options = c("striped", "hold_position"))
```

>>>>

```{r}
sim_summary_stat_cap <- paste0(
  "Summary statistics of the food-web and stability metrics.") %>%
  str_replace_all("\\s+", " ")
tar_read(tab_sim_summary_stat) %>%
  rename_with(~str_replace_all(.x, "\\%", "\\\\%")) %>%
  kable(
    booktabs = TRUE,
    format = "latex",
    escape = FALSE,
    caption = sim_summary_stat_cap,
    label = "param") %>%
  column_spec(1, bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major", valign = "middle") %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

@@

```{r}
tar_read(tab_sem_doak_eff) %>%
  kable(booktabs = TRUE,
    format = "latex",
    caption = "Standardised estimates from the Structural Equation Model
    displayed in main text (Fig. 2).",
    label = "sem-coeff"
    ) %>%
collapse_rows(columns = 1, latex_hline = "major", valign = "middle") %>%
kable_styling(latex_options = c("striped", "hold_position"))
```
